An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-11-30 latex-spie/article.tex
minor changes

>>>>

manually annotated, each frame is considered as a different location, similar frame sensitivity is approx 10 frame.
Moving platform,
indoor
Kinect (grayscale and depth images) 
Kinect: max line of sight is 10m
Average speed is approx 0.5 m/s 
bright, dim, dark (to evaluate depth info)
bright 2082, dim 2083, dark 2251
approx 1000 frames per loop
2 loops, each dataset approx 2000 frames
1 loop for loop closure testing
examples shown in \ref{fig:dataset}
